The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-28 sandbox/note_km.tex
km note: notation improvement, technical kvetching

\begin{align}
	N_{\rm det}^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a; r, M; q)\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
	\alpha}\,f(q)\,\Lambda^1(r_a/\alpha, M\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\alpha(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	N_{\rm det}^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
    \\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
    \\
    &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\beta) \Lambda^2(r,qM\a) 
    p_{\rm tra}(qM\a) \\
	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
	\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2(r_a/\beta, qM\a)\,p_{\rm 
	tra}(qM\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\beta(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }.
\end{equation}

@@

Note again that the denominators of $\Lambda\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent occurrence,
\begin{align}
\Lambda\a(r\a,M\a) &= 
    \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
    \sum_i N_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to
\begin{align}
\notag
\Lambda\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
   \left\{ \Lambda^0(r\a, M\a)+ 
\mu(\mathrm{BF}, M\a)
\left[ \int {\mathrm{d}q \over \alpha}\,f(q)\,\Lambda^1\left({r\a\over 
    \alpha}, 
M\a\right)\,
\right.   
   \right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over \beta}\,f(q)\,\Lambda^2\left({r\a\over \beta}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.  
\end{align}

@@

We have $f(q)=\delta(q-1)$. Thus
\begin{align}
	\Lambda\a(r\a, M\a)
	={1\over 1+\mu(\mathrm{BF}, M\a)}
	\left\{\Lambda^0(r\a, M\a)
	%+\mathrm{BF}\cdot 2^{3/2}\sqrt{2}\left[\Lambda^1(\sqrt{2}\,r\a, M\a)+\Lambda^2(\sqrt{2}\,r\a, M\a)\right].
	+\mu(\mathrm{BF}, M\a)\cdot\sqrt{2}\left[\Lambda^1(\sqrt{2}\,r\a, M\a)+\Lambda^2(\sqrt{2}\,r\a, M\a)\right]
	\right\},
\end{align}
where
\begin{equation}
	\mu(\mathrm{BF}, M\a)=\int \mathrm{d}q\,f(q) {\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2}
	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
\end{equation}

@@

If $\Lambda^i(r, M)=Z^i\cdot\delta(r-r_0)$ (all the planets have the same radius),
\begin{align}
	\Lambda\a(r\a, M\a)
	%=\Lambda_0\left[(1-\mathrm{BF})\cdot\delta(r\a-r_0)
	%+2\mathrm{BF}\cdot 2^{3/2}\cdot\delta\left(r\a-{r_0\over\sqrt{2}}\right)\right].
	={1 \over 1+\mu(\mathrm{BF})}
	\left[Z^0 \cdot \delta(r\a-r_0)+(Z^1+Z^2)\cdot \mu(\mathrm{BF})\cdot \delta\left(r\a-{r_0\over\sqrt{2}}\right)\right].
\end{align}
This reproduces Eq.(9) of the draft, after correcting for the smaller number of apparently searchable stars for the diluted planets (factor of $(1/2)^3$). In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields $\Lambda\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.

@@

If we assume 
\begin{equation}
	L(M) \sim M^\alpha \sim R^\alpha,
\end{equation}
we find
\begin{align}
	A=(1+q^\alpha)^{-1/2}, \quad 
	B=q^{-1}(1+q^{-\alpha})^{-1/2},
\end{align}
so
\begin{align}
	\Lambda\a(r\a, M\a)=...
	%&=(1-\mathrm{BF})\cdot\Lambda^0(r\a, M\a)\\
	%&+\mathrm{BF}\cdot 
	%\int \mathrm{d}q\,f(q)
	%(1+q^\alpha)^2 \cdot \Lambda^1\left( r\a\sqrt{1+q^\alpha}, M\a\right)\\
	%&+\mathrm{BF}\cdot
	%\int {\mathrm{d}q}\,f(q)q^{8/3}
	%\sqrt{1+q^{-\alpha}}(1+q^\alpha)^{3/2}
	%\cdot\Lambda^2\left(r\a q\sqrt{1+q^{-\alpha}}, qM\a\right).
\end{align}
We may further assume
\begin{equation}
	f(q)\sim q^\beta, \quad \Lambda(r) \sim r^\gamma
\end{equation}
and keep calculating...

>>>>

\begin{align}
	N_{\rm det}^1(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^1(r\a, M\a; r, M)
	\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, q}^1(r\a, M\a; r, M; q)\cdot\Lambda^1(r, M) \cdot p_{\rm tra}(M)\\
	&=N\s^0(\delta_{\rm obs}, L(M\a))\cdot p_{\rm tra}(M\a) \cdot
	\mu(\mathrm{BF}, M\a) \int {\mathrm{d}q \over 
	\mathcal{A}}\,f(q)\,\Lambda^1(r_a/\mathcal{A}, M\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}.
\end{equation}

Finally,
\begin{align}
	N_{\rm det}^2(r\a, M\a)
	&=\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{\rm s}^2(r\a, M\a; r, M)
	\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
    \\
	&=\int \mathrm{d}q\,f(q)\int\mathrm{d}r\mathrm{d}M\,\mathcal{N}_{{\rm s}, 
	q}^2(r\a, M\a; r, M; q)\cdot\Lambda^2(r, M) \cdot p_{\rm tra}(M)
    \\
    &= N\s^0(\delta_{\rm obs},L(M\a)) \mu({\rm BF},M\a)
    \int {\rm d}r{\rm d}q\, q f(q) \delta(r_a - r\mathcal{B}) 
    \Lambda^2(r,qM\a) 
    p_{\rm tra}(qM\a) \\
	&=%N_{\rm s}(\delta_{\rm obs}, L(M_a)
	N\s^0(\delta_{\rm obs}, L(M\a))\cdot\mu(\mathrm{BF}, M\a)
	\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Lambda^2(r_a/\mathcal{B}, 
	qM\a)\,p_{\rm 
	tra}(qM\a),
	%\left[L_{\rm sys}(M_a, q) \over L(M_a) \right]^{3/2},
\end{align}
where
\begin{equation}
	\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
	sys}(M\a, q)} }.
\end{equation}

@@

Note again that the denominators of $\Lambda\a$ are the same for singles, 
primaries, and secondaries: $N_{\rm s,a}(\delta_{\rm obs}, M\a)$ and $p_{\rm 
tra}(M\a)$. This is because we are calculating the occurrence at the same 
apparent planet/star properties, and the observer can never distinguish 
binaries from singles (and adopt the primary properties for binaries).
Using the results above, the apparent occurrence rate,
\begin{align}
\Lambda\a(r\a,M\a) &= 
    \frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
    \sum_i N_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to
\begin{align}
\notag
\Lambda\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
   \left\{ \Lambda^0(r\a, M\a)+ 
\mu(\mathrm{BF}, M\a)
\left[ \int {\mathrm{d}q \over \mathcal{A}}\,f(q)\,\Lambda^1\left({r\a\over 
    \mathcal{A}}, 
M\a\right)\,
\right.   
   \right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over \mathcal{B}}\,f(q)\,\Lambda^2\left({r\a\over 
\mathcal{B}}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.  
\end{align}

\subsubsection{Simplifying above general result}
To simplify, drop the explicit $M_a$ and BF 
dependences, and assume $R\propto M$, so $R(qM_a)/R(M_a) = q$.
Also, move all superscript numbers to subscripts.
Then the apparent occurrence rate is
\begin{equation}
\Lambda\a(r\a) = \frac{1}{1+\mu}
\left(
    \Lambda_0(r\a) +
    \mu \left[
        \int \frac{{\rm d}q}{\mathcal{A}(q)} f(q) 
        \Lambda_1\left( \frac{r\a}{\mathcal{A}(q)} \right)
        +
        \int \frac{q {\rm d}q}{\mathcal{B}(q)} f(q)
        \Lambda_2\left(\frac{r\a}{\mathcal{B}(q)}\right) q^{2/3}
    \right]
\right).
\end{equation}
For the power law case when $L\sim M^\alpha$,
\begin{equation}
\mathcal{A}(q)
=(1+q^\alpha)^{-1/2},
\quad
\mathcal{B}(q)
=q^{-1}(1+q^{-\alpha})^{-1/2}
\end{equation}

@@

We have $f(q)=\delta(q-1)$. The apparent rate is
\begin{align}
\Lambda\a(r\a)
={1\over 1+\mu(\mathrm{BF})}
\left\{\Lambda_0(r\a)
+\mu(\mathrm{BF})\cdot \sqrt{2}\cdot\left[\Lambda_1(\sqrt{2}\,r\a)
+\Lambda_2(\sqrt{2}\,r\a)\right]
\right\},
\end{align}
where
\begin{equation}
	\mu(\mathrm{BF})=\int \mathrm{d}q\,f(q) 
	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
	L(M\a)}\right]^{3/2}
	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
\end{equation}

@@

If $\Lambda_i(r, M)=Z_i\cdot\delta(r-r_0)$ (all the planets have the same 
radius), by using the identity $\delta(ax+b)=\delta(x+b/a)/|a|$,
\begin{align}
	\Lambda\a(r\a)
	={1 \over 1+\mu(\mathrm{BF})}
	\left[Z_0 \cdot \delta(r\a-r_0)+(Z_1+Z_2)\cdot \sqrt{2} 
	\mu(\mathrm{BF})\cdot 
	\delta\left(r\a-\frac{r_0}{\sqrt{2}}\right)\right].
    \label{eq:model1_apparent_rate}
\end{align}
This reproduces Eq.(9) of the draft (after removing the $p_{\rm det}$ terms).
In the limit of $\mathrm{BF}\to1$ ($\mu\to\infty$), the above formula yields 
$\Gamma\a=(Z^1+Z^2)\,\delta(r\a-{r_0/\sqrt{2}})$.

Eq.~\ref{eq:model1_apparent_rate} is technically abusing notation, because 
$\Lambda$ must be dimensionless, and $\delta(r-r_0)$ has units 
of inverse length.
Since the equation is meant to convey the idea: ``at a given apparent radius, 
the apparent number of planets per star is $x$'', and the delta function is 
more succinct than listing out discrete cases, we leave it as-is.

@@

If we assume 
\begin{equation}
	L(M) \sim M^\alpha \sim R^\alpha,
\end{equation}
we find
\begin{align}
	A=(1+q^\alpha)^{-1/2}, \quad 
	B=q^{-1}(1+q^{-\alpha})^{-1/2},
\end{align}
so
\begin{align}
	\Lambda\a(r\a, M\a)=...
	%&=(1-\mathrm{BF})\cdot\Lambda^0(r\a, M\a)\\
	%&+\mathrm{BF}\cdot 
	%\int \mathrm{d}q\,f(q)
	%(1+q^\mathcal{A})^2 \cdot \Lambda^1\left( r\a\sqrt{1+q^\mathcal{A}}, 
	%M\a\right)\\
	%&+\mathrm{BF}\cdot
	%\int {\mathrm{d}q}\,f(q)q^{8/3}
	%\sqrt{1+q^{-\mathcal{A}}}(1+q^\mathcal{A})^{3/2}
	%\cdot\Lambda^2\left(r\a q\sqrt{1+q^{-\mathcal{A}}}, qM\a\right).
\end{align}
We may further assume
\begin{equation}
	f(q)\sim q^\beta, \quad \Lambda(r) \sim r^\gamma
\end{equation}
and keep calculating...
